Objectification in Action: Self- and Other-Objectification in Same-gender Interactions

### 2020-09-07 Final_Manuscript.Rmd
added Asha's edits

##Self-Objectification
Self-objectification is a psychological process that accounts offer a cognitive mechanism for translating the experiences of interpersonal objectification [@loughnan2015exploring] to negative mental health outcomes (e.g., anxiety, self-esteem, and cognitive performance) [@calogero2011; @moradi2008]. @calogero2011 proposes that self-objectification can be conceptualized as a learned trait, or *trait* self-objectification (TSO). Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines [@morry2001magazine], or when wearing sexualizing clothing [@fredrickson1998swimsuit]. This momentary self-objectification is referred to as *state* self-objectification [@bernard2018bodies; @calogero2011; @moradi2008]. Being objectified by another person may interact TSO to effect experiences of feeling like a body, or state self-objectification [SSO; @garcia2016objectification].

@@

Past research has focused on men’s objectifying behaviors, with little attention to the role that women may also play in objectifying other women. @hill2008examining assessed women’s experiences of objectification from men separately from women’s experiences of objectification from women and found that women may be socialized not only to see themselves as objects but perhaps to see other women as objects as well, although this process was not comfirmed to occur during an actual interpersonal interaction. @loughnan2015exploring found that women objectify other women to a greater extent than they objectify men. Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but we know very little about interpersonal sexual objectification among women and what the immediate effects of this objectification might be. We do know that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, if women objectify other women, perhaps even to a stronger degree than they objectify men, this higher dose of objectification might be a detrimental combination.

##Interpersonal Objectification
Studies have shown that within social encounters women are gazed at more than men [@briton1995], and often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on their physical self [@puvia2013being; @young1979]. Moreover, perhaps the most adverse effect is that it effectively socializes girls and women to treat themselves as objects to be looked at and evaluated [@Bartky; @berger1972; @fredrickson1998swimsuit]. @gervais2020social recently reviewed the research on interpersonal objectification and organized our current theoretical understanding of this process in the Social Interaction Model of Objectification (SIMO). What is clear from @gervais2020social is that we know little about women-on-women interpersonal objectification. Could there also be negative consequences of this type of interpersonal objectification? Perhaps women could be amplifying each others' state self-objectification as they get ready to go out for the night [EDIT??], *before* the theoretical encounters with men organized in the SIMO occur. In this way, women's rituals of getting ready together might place even women with low TSO in a higher SSO group. [Kat: This has me thinking about the difference between objectification in a romantic setting (which was the setting created in the initial experiment) vs objectification in a platonic setting/between friends. Might be useful to discuss this difference, or just have a sentence here that clarifies objectification can occur within non-sexual settings]

Interpersonal objectification can also occur within the context of romantic relationships, in addition to interactions with strangers. Among heterosexual male and female college students, self-objectification has been found to be positively associated with the extent to which they objectify their romantic partners [@zurbriggen2011self]. Researchers have also studied interpersonal objectification and self-objectification in romantic relationships [@strelan2018birds]. Evidence is mixed, suggesting that women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship. There is also evidence that they experience less SSO after appearance comments within romantic relationships [@meltzer2020women], but less is known about first dates. An important caveat to this literature is that it is only about heterosexual relationships. A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [CITE PWQ paper I reviewed, Yoder editor]. Both romantic relationships and relationships in general have been studied in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.

@@

##Interpersonal Objectification and Authenticity
There is some evidence that reduced authenticity is a consequence of self-objectification in the moment [@garcia2016objectification; again CITE PWQ paper I reviewed, Yoder editor]. This link has been justified by the literature on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting], viewing the experience of being objectified in an interaction as an identity threat situation [@miles2015stop; @nadal2012effects]. Further, empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal]. When a woman is objectified by a man, and subsequently experiences self-objectification, the intergroup nature of this encounter might trigger identity threat. Thus, perhaps there are fewer negative consequences when a woman is objectified by another woman, that is, woman-woman interpersonal objectification processes might diverge from mix-gender interpersonal objectification processes precisely because they are not intergroup interactions (at least with respect to gender identity). A woman objectified by another woman may not be having the same negative consequences that cascade from situations that trigger group-based identity threat [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in any interaction (intergroup or ingroup) may be enough to reduce women's feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; PWQ paper I reviewed, Yoder editor].

##The Current Study
In the current study, we sought to examine what occurs during an interaction in which one or both partners are objectifying each other, similarly to @garcia2016objectification, but between same-gender interpersonal interactions among women. Moreover, the current study uses a face-to-face interaction paradigm and dyadic data analysis techniques to examine the effects for both women simultaneously. Although the literature on woman-woman objectification is small, mixed, and does not cover interpersonal encourters, we expected to replicate some of the results found in @garcia2016objectification. Most importantly, we predicted that being objectified by one’s interaction partner would lead to self-objectification. We also expected, in line with @garcia2016objectification, that TSO would moderate this relationship, amplifying the positive assocaition between being objectified and SSO for women higher in TSO. We hypothesized that SSO would, in turn, lead to feelings of inauthenticity [although there is ample support against this prediction from the identity threat within intergroup interactions literature; @rollero2016bringing]. Further, we hypothesized that these feelings of inauthencity would then be associated with reduced feelings of agency in romantic relationships, reduced career aspiration, and reduced cognitive performance. In summary, we expected to find a positive relationship between other-objectification by one's partner and state self-objectification. We also expected to find a negative relationship between self-state objectification and interaction authenticity, and that interaction authenticity will be positively related to cognitive performance, relationship agency, and career aspirations.

@@

##Procedure
The procedure used was identical to that in @garcia2016objectification, except for the instructions that the participants were given. In brief, that methodology is that each participant arrived at the laboratory and were then led into separate cubicles to prevent any communication between the participants before the interaction. In addition, each participant was screened for prior acquaintance to confirm that they had not met prior to the study. They were asked to sign the consent form to participate, and the study was described as follows: “This is a study looking at how students form different types of relationships at college.” A prompt on the computer screen told the participants that they were assigned to the “College Relationships” condition and gave the following instructions:

@@

*All* participants were told that they were assigned to the "College Relationships" condition. Self-objectification has been found to occur after a mere relationship prime among women [@sanchez2008romance] because, in Westurn culture and beyond, women need to look attractive to obtain and maintain successful relationship, thus, the "College Relationships" condition may heighten self-objectification and the evaluation of other women in a sexualized way. The decision was made to ask even heterosexual women to judge their fellow-woman partners for their potential as romantic partners. We felt that this prompt would keep the study closest to a replication of the previous @garcia2016objectification version of the study, and amplify the potential for objectification that would normally be low in the context of a psychology laboratory. Recall that, past research has found that women are indeed able to evaluate other women's potential as romantic partners [i.e., their sexual attractiveness; CITE]---indeed, women may be unfortunately quite used to thinking about their own "datability," and we suspect this this habitual thought pattern will translate to their thoughts about other women.

@@

```{r 2016figure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads."}
include_graphics("2016_figure.jpg")
```
This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used a dyadic path analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO). See Figure\ \@ref(fig:2016figure) for the results of the analysis from this previous study. We hope to investigate how the central effects found in the previous study relate to interactions between two women. Specifically, we are interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, affects feelings of inauthenticity during the interaction. In addition, we will also test if the effect of other-objectification in an interaction on SSO is only present for those women who are high in trait self-objectification, as in @garcia2016objectification. Further, we will investigate the relationships between experiencing interaction inauthenticity and relationship agency, career aspirations, and cognitive performance.

While @garcia2016objectification used dyadic path analysis, we will conduct our dyadic analyses using multilevel modeling. Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structural Equation Modeling (SEM) than it is for indistinguishable dyads (e.g., same-gender interacting pairs) [@ledermann2017analyzing; @garcia2015moderation]. One reason for this asymmetry is that, due to the arbitrary distinctions made between "partner 1" and "partner 2" in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means) for indistinguishable dyads but these equality constraints should not then be considered in the degrees of freedom calculations for fit estimations [@olsen2006structural]. Further, @olsen2006structural detail how a new independence model and the corresponding fit measure should be re-calculated for indistinguishable dyads models. The current study uses dyadic multilevel modeling (MLM) to test all relationships and mediation patterns. The online supplementary materials contains analysis using SEM. See @ledermann2017analyzing for a more complete discussion of the considerations for using SEM versus MLM for dyadic analysis.

@@

Before moving to the main analyses, we discuss statistical equivalence test that provide support for combining Sample 1 and Sample 2 in one analysis sample. The online supplemental material contains the main analyses separated by samples. All results presented below are from models including sample as a control variable.

@@

#Discussion
The current study tested whether the model of interpersonal objectification and state self-objectification (SSO) used in @garcia2016objectification replicates in a same-gender dyadic sample of women only. Although past research has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if *interpersonal* other-objectification by women is related to state self-objectification in their woman-identified interaction partners. As hypothesized, the current study did find a significant relationship between a woman's interaction partner's report of having objectified her and her own post-interaction feelings of self-objectification. That is, there was a significant partner effect of other-objectification on SSO. This effect extends the equivalent relationship found in mixed-gender interactions to the context of same-gender interactions between women. Thus, it could be that it is not only the male gaze, and male other-objectification that is related to women's state self-objectification, but being objectified by another woman can also result in SSO, at least in the context of a scenario where they know they are being evaluated as a potential dating partner.

As is the case in all correlational studies, we cannot be sure in the causal direction. It could be that women's SSO causes them to be objectified by their interaction partner. This interpretation is theoretically interesting given that, in both the @garcia2016objectification study and in the current study, it is *women's* SSO that relates to being objectified by one's partner. However, Objectification Theory [@robertsfredrickson], as well as past experimental studies [@saguyetal2010; CITE], suggest that the causal flow is from other-objectification to SSO. Although, the current study found evidence for the partner effect of other-objectification on SSO, there was a lack of evidence for the connections between SSO and downstream negative consequences.

Where the results of the current study diverge most notably from the results of studies testing interpersonal objectification among mixed-gender dyads is the lack of evidence for relationships between SSO and interaction inauthenticity. In addition, we found no evidence of *direct* or *indirect* relationships between SSO and cognitive functioning, relationship agency, and career aspirations. Nor was there evidence of *direct* or *indirect* relationships between other-objectification and any of these outcomes. This is somewhat suprising given the plentiful evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; @quinn2011performance; and see @moradi2008 for a review] and the small, but extant research on interpersonal other-ojectification and cognitive functioning [@logel2009interacting; @garcia2016objectification]. This lack of evidence could potentially signal diverging processes between women's experiences with interpersonal objectification from men and interpersonal objectification from women. There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you; @gervais2013my], and perhaps the self-objectification experienced within an interaction with a women is not as harmful as the self-objectification experienced within an interaction with a man. However, as a strong note of caution, we need to be careful not to interpret a null result as evidence of no relationship.

@@

Although we did not find a connection between SSO and authenticity, we did find significant positive relationships between authenticity and relationship agency and career aspirations. The relationship between authenticity and cognitive functioning was also estimated as positive, but was not statistically signficant. Again, due to the lack of connection between SSO and authenticity, we found no evidence of *indirect* relationships between SSO and these outcome variables. This evidence of a relationship between authenticity and the relational outcome variables (i.e., relationship agency and career aspirations) provides evidence that corroborates past findings that felt authenticity in interactions is important for healthy relationship functioning [@garcia2016objectification; PWQ paper I reviewed]. Just as authenticity has been found to be important in intergroup interactions [@brunelletal2010; @garcia2016objectification; @tolman2006looking], we again find more evidence here that disruptions in feelings of authenticity can negatively impact relationships beyond the current partner. Although the current study did not find a connection between authenticity and SSO, this seems theoretically to be a natural connection, and more work needs to be done to discover when and how SSO leads to inauthenticity in interpersonal objectification situations.

@@

###Sexual Objectification and the Objectifyer's Gender
The current sample contained a mixture of heterosexual and non-heterosexual women, but all participants were asked to think about and evaluate their partner as a potential dating partner. We think that hetereosexual women are able to do this with other women as their target---and there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---they may be even more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women). This differential psychological process between women with differing sexualities might have served to dampen our ability to detect relationships, adding variability. [Kat: The only other thing I would add re: sexuality limitations are that we didn’t collect/use sexual orientation, so we couldn’t analyze results by that at all/our samples might have differed there.]

@@

##Clinical Implications
The results from the current analysis highlight how subtle forms of sexist discrimination operate to inform prevention and intervention efforts in both clinical and educational contexts. These results are quite useful for promoting mental health and within early action programs for girls and young women, where scholars and practitioners might provide the tools necessary to circumvent or mitigate negative effects on self-objectification, and combat such experiences.

#Conclusion
The results of this study demonstrate the complex and ambivalent nature of sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being. We did not find a significant effect between actor SSO and felt authenticity in the interaction, which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to interaction inauthenticity. Perhaps women could be amplifying each others' self-objectification as they get ready to go out for the night, *before* the theoretical encounters with men outlined in @gervais2020social occur.

>>>>

##Self-Objectification
Self-objectification is a psychological process that provides a cognitive mechanism to translate the experiences of interpersonal objectification [@loughnan2015exploring] to negative mental health outcomes (e.g., anxiety, self-esteem, and cognitive performance) [@calogero2011; @moradi2008]. @calogero2011 proposes that self-objectification can be conceptualized as a learned trait, or *trait* self-objectification (TSO). Furthermore, it can also be elicited momentarily, through the media, for example, with sexualized images in movies and magazines [@morry2001magazine], or when wearing sexualizing clothing [@fredrickson1998swimsuit]. This momentary self-objectification is referred to as *state* self-objectification [@bernard2018bodies; @calogero2011; @moradi2008]. Being objectified by another person may interact TSO to effect experiences of feeling like a body, or state self-objectification [SSO; @garcia2016objectification].

@@

[Asha comment on next paragraph: Hill and Fischer (2008) assessed women’s experiences of objectification from men separately from women’s experiences of objectification from women, and found that women may be socialized not only to see themselves as objects, but perhaps to see other women as objects as well, although this process was not comfirmed to occur during an actual interpersonal interaction

Could this sentence be written like:

Though, when Hill and Fischer(2008) assessed women’s experiences of objectification from men independently from that of women, they found that women are likely to be socialized to not only to see themselves s objects, but potentially see other women as objects as well. This process ,however, was not confirmed to occur during an interpersonal interaction.]

Past research has focused on men’s objectifying behaviors, with little attention paid to the role that women may also play in objectifying other women. @hill2008examining assessed women’s experiences of objectification from men separately from women’s experiences of objectification from women and found that women may be socialized not only to see themselves as objects but perhaps to see other women as objects as well, although this process was not comfirmed to occur during an actual interpersonal interaction. @loughnan2015exploring found that women objectify other women to a greater extent than they objectify men. Women have also been found to objectify (dehumanized) sexualized targets presented as images [@puvia2013being], but very little is known about interpersonal sexual objectification among women and what the proximal effects of this objectification might be. We do know that objectification has more adverse consequences for women than men [@gervais2011you; @moradi2008; @saguyetal2010], however, if women objectify other women, perhaps even to a stronger degree than they objectify men, this higher level of objectification might be a detrimental combination.

##Interpersonal Objectification
Studies have shown that within social encounters women are gazed at more than men [@briton1995], and often times feel ‘looked at’ within interpersonal interactions [@argyle1969; @miles2015stop], and will more than likely internalize the objectifying gaze on their physical self [@puvia2013being; @young1979]. Moreover, perhaps the most adverse effect is that it socializes girls and women to treat themselves as objects to be looked at and evaluated [@Bartky; @berger1972; @fredrickson1998swimsuit]. @gervais2020social recently reviewed the research on interpersonal objectification and organized our current theoretical understanding of this process in the Social Interaction Model of Objectification (SIMO). What is clear from @gervais2020social is that we know little about women-on-women interpersonal objectification. Could there also be negative consequences of this type of interpersonal objectification? Perhaps women could be amplifying each others' state self-objectification as they get ready to go out for the night [EDIT??], *before* the theoretical encounters with men organized in the SIMO occur. In this way, women's rituals of getting ready together might place even women with low TSO in a higher SSO group. [Kat: This has me thinking about the difference between objectification in a romantic setting (which was the setting created in the initial experiment) vs objectification in a platonic setting/between friends. Might be useful to discuss this difference, or just have a sentence here that clarifies objectification can occur within non-sexual settings] [Asha: I think this is a great way to illustrate the potential experience but when I read it I was kind of like “wait, when did we talk about women going out?”]

Interpersonal objectification can also occur within the context of romantic relationships, in addition to interactions with strangers. Among heterosexual male and female college students, self-objectification has been found to be positively associated with the extent to which they objectify their romantic partners [@zurbriggen2011self]. Researchers have also studied interpersonal objectification and self-objectification in romantic relationships [@strelan2018birds]. Evidence is mixed, suggesting that women can sometimes have positive outcomes from appearance valuation within the context of an established romantic relationship. There is also evidence that they experience less SSO after appearance comments within romantic relationships [@meltzer2020women], but less is known about first dates. An important caveat to this literature is that it is only about heterosexual relationships. A recent study has investigated the effect of self-objectification on the reduction of relationship building skills in general (including same-sex friendships) [CITE PWQ paper I reviewed, Yoder editor]. Both romantic relationships and stranger encounters have been studied in the context of objectification, but neither of these literatures have investigated specifically same-gender relationships.

@@

##Interpersonal Objectification and Authenticity
There is some evidence that reduced authenticity is a consequence of self-objectification in the moment [@garcia2016objectification; again CITE PWQ paper I reviewed, Yoder editor]. This link has been justified by the literature on stigmatized-stigmatizer interactions [@hebl2005promoting; @richeson2003prejudice; @shelton2005expecting], viewing the experience of being objectified in an interaction as an identity threat situation [@miles2015stop; @nadal2012effects]. Further, empirical evidence reveals that objectification manifests through inauthenticity in romantic relationships [@brunelletal2010], adverse attitudes in regard to career aspirations, and a decrease in concentration and impairment in female cognitive performance [@kahalon2018don; @quinnetal]. When a woman is objectified by a man, and subsequently experiences self-objectification, the intergroup nature of this encounter might trigger identity threat. Thus, perhaps there are fewer negative consequences when a woman is objectified by another woman, specifically, woman-woman interpersonal objectification processes might diverge from mix-gender interpersonal objectification processes precisely because they are not intergroup interactions (at least with respect to gender identity). A woman objectified by another woman may not be having the same negative consequences that cascade from situations that trigger group-based identity threat [@deaux1987putting; @dovidio2006nonverbal; @hebl2005promoting], but feeling like a body, rather than a full human, in any interaction (intergroup or ingroup) may be enough to reduce women's feelings of authenticity and social competence, regardless of the gender of the objectifyer [@tolman2006looking; PWQ paper I reviewed, Yoder editor].

##The Current Study
In the current study, we sought to examine what occurs during an interaction in which one or both partners are objectifying each other, similarly to @garcia2016objectification, but between same-gender interpersonal interactions among women. Moreover, the current study uses a face-to-face interaction paradigm and dyadic data analysis techniques to examine the effects for both women simultaneously. Although the literature on woman-woman objectification is small, the results are mixed, and does not cover interpersonal encourters, we expected to replicate some of the results found in @garcia2016objectification. Most importantly, we predicted that being objectified by one’s interaction partner would lead to self-objectification. We also expected, in line with @garcia2016objectification, that TSO would moderate this relationship, amplifying the positive assocaition between being objectified and SSO for women higher in TSO. We hypothesized that SSO would, in turn, lead to feelings of inauthenticity [although there is ample support against this prediction from the identity threat within intergroup interactions literature; @rollero2016bringing]. Further, we hypothesized that these feelings of inauthencity would then be associated with reduced feelings of agency in romantic relationships, reduced career aspiration, and reduced cognitive performance. In summary, we expected to find a positive relationship between other-objectification by one's partner and state self-objectification. We also expected to find a negative relationship between self-state objectification and interaction authenticity, and that interaction authenticity will be positively related to cognitive performance, relationship agency, and career aspirations.

@@

##Procedure
Except for the instructions given to participants, the procedure used was identical to that in @garcia2016objectification. In brief, that methodology is that each participant arrived at the laboratory and were then led into separate cubicles to prevent any communication between the participants before the interaction. In addition, each participant was screened for prior acquaintance to confirm that they had not met prior to the study. They were asked to sign the consent form to participate, and the study was described as follows: “This is a study looking at how students form different types of relationships at college.” A prompt on the computer screen told the participants that they were assigned to the “College Relationships” condition and gave the following instructions:

@@

*All* participants were told that they were assigned to the "College Relationships" condition. Self-objectification has been found to occur after a mere relationship prime among women [@sanchez2008romance] because, in Westurn culture and beyond, women need to look attractive to obtain and maintain successful relationship, thus, the "College Relationships" condition may heighten self-objectification and the evaluation of other women in a sexualized way. The decision was made to ask even heterosexual women to judge their fellow-woman partners for their potential as romantic partners. We felt that this prompt would keep the study closest to a replication of the previous @garcia2016objectification version of the study, and strengthen the potential for objectification that would normally be low in the context of a psychology laboratory. Recall that, past research has found that women are indeed able to evaluate other women's potential as romantic partners [i.e., their sexual attractiveness; CITE]---indeed, women may be unfortunately quite used to thinking about their own "datability," and we suspect this this habitual thought pattern will translate to their thoughts about other women.

@@

```{r 2016figure, include=TRUE, echo=FALSE, results='asis', out.width="400px", fig.cap="Path Analysis Model from Garcia et al. (2016) study with distinguishable dyads."}
include_graphics("2016_figure.jpg")
```
This study sought to replicate the results of @garcia2016objectification’s study, done with male-female pairs, which used a dyadic path analysis to detect whether partners’ objectification of one another affected state self-objectification (SSO). See Figure\ \@ref(fig:2016figure) for the results of the analysis from this previous study. We investigated how the central effects found in the previous study relate to interactions between two women. Specifically, we are interested in testing the relationship between state-other objectification and SSO, and how SSO in turn, affects feelings of inauthenticity during the interaction. In addition, we will also test if the effect of other-objectification in an interaction on SSO is only present for those women who are high in trait self-objectification, as in @garcia2016objectification. Further, we will investigate the relationships between experiencing interaction inauthenticity and relationship agency, career aspirations, and cognitive performance. [Asha: This section feels like a mixture of explaining what the study was intended to investigate as wel as future directions. Is that the point, or can this be organized better?]

While @garcia2016objectification used dyadic path analysis, the current study used multilevel modeling for our dyadic analyses. Dyadic analyses for distinguishable dyads (e.g., mixed-gender interacting pairs) is more natural in Structural Equation Modeling (SEM) than it is for indistinguishable dyads (e.g., same-gender interacting pairs) [@ledermann2017analyzing; @garcia2015moderation]. One reason for this asymmetry is that, due to the arbitrary distinctions made between "partner 1" and "partner 2" in indistinguishable dyads, many estimates need to be fixed to be equal (i.e., paths, variances, covariances, endogenous intercepts, and exogenous means) for indistinguishable dyads but these equality constraints should not then be considered in the degrees of freedom calculations for fit estimations [@olsen2006structural]. Further, @olsen2006structural detail how a new independence model and the corresponding fit measure should be re-calculated for indistinguishable dyads models. The current study uses dyadic multilevel modeling (MLM) to test all relationships and mediation patterns. The online supplementary materials contains analysis using SEM. See @ledermann2017analyzing for a more complete discussion of the considerations for using SEM versus MLM for dyadic analysis.

@@

Before moving to the main analyses, we discuss statistical equivalence tests that provide support for combining Sample 1 and Sample 2 in one analysis sample. The online supplemental material contains the main analyses separated by samples. All results presented below are from models including sample as a control variable.

@@

#Discussion
The current study tested whether the model of interpersonal objectification and state self-objectification (SSO) used in @garcia2016objectification replicates in a same-gender dyadic sample of women only. Although past research has found that women do objectify other women [@puvia2013being; @loughnan2015exploring; @harsey2020men], this is the first study to test if *interpersonal* other-objectification by women is related to state self-objectification in their woman-identified interaction partners. As hypothesized, the current study did find a significant relationship between a woman's interaction partner's report of having objectified her and her own post-interaction feelings of self-objectification. That is, there was a significant partner effect of other-objectification on SSO. This effect extends the equivalent relationship found in mixed-gender interactions to the context of same-gender interactions between women. Thus, evidence suggests that it is not only the male gaze, and male other-objectification that is related to women's state self-objectification, but being objectified by another woman can also result in SSO, at least in the context of a scenario where they know they are being evaluated as a potential dating partner. [Asha:Or … thus evidence provides support for the claim that women being objectified by another woman result in sso in ways that are not uniquely dissimilar from that of xyz]

As is the case in all correlational studies, we cannot be sure about the causal direction. It could be that women's SSO causes them to be objectified by their interaction partner. This interpretation is theoretically interesting given that, in both the @garcia2016objectification study and in the current study, it is *women's* SSO that relates to being objectified by one's partner. However, Objectification Theory [@robertsfredrickson], as well as past experimental studies [@saguyetal2010; CITE], suggest that the causal flow is from other-objectification to SSO. Although, the current study found evidence for the partner effect of other-objectification on SSO, there was a lack of evidence for the connections between SSO and downstream negative consequences.

Where the results of the current study diverge most notably from the results of studies testing interpersonal objectification among mixed-gender dyads is the lack of evidence for relationships between SSO and interaction inauthenticity. In addition, we found no evidence of *direct* or *indirect* relationships between SSO and cognitive functioning, relationship agency, and career aspirations. Nor was there evidence of *direct* or *indirect* relationships between other-objectification and any of these outcomes. This is somewhat suprising given the extant evidence linking SSO and cognitive functioning [@fredrickson1998swimsuit; @quinn2011performance; and see @moradi2008 for a review] and the small, but extant research on interpersonal other-ojectification and cognitive functioning [@logel2009interacting; @garcia2016objectification]. This lack of evidence could potentially signal diverging processes between women's experiences with interpersonal objectification from men and interpersonal objectification from women. There is quite a bit of evidence suggesting that the male gaze is particularly detrimental [@calogero2004test; @robertsfredrickson; @gervais2011you; @gervais2013my], and perhaps the self-objectification experienced within an interaction with a women is not as harmful as the self-objectification experienced within an interaction with a man. As a strong note of caution, it is best not to interpret a null result as evidence of no relationship.

@@

Although we did not find a connection between SSO and authenticity, we did find significant positive relationships between authenticity and relationship agency, and authenticity and career aspirations. The relationship between authenticity and cognitive functioning was also estimated as positive, but was not statistically signficant. Again, due to the lack of connection between SSO and authenticity, we found no evidence of *indirect* relationships between SSO and these outcome variables. This evidence of a relationship between authenticity and the relational outcome variables (i.e., relationship agency and career aspirations) provides evidence that corroborates past findings that felt authenticity in interactions is important for healthy relationship functioning [@garcia2016objectification; PWQ paper I reviewed]. Just as authenticity has been found to be important in intergroup interactions [@brunelletal2010; @garcia2016objectification; @tolman2006looking], we again find more evidence here that disruptions in feelings of authenticity can negatively impact relationships beyond the current partner. Although the current study did not find a connection between authenticity and SSO, this seems theoretically to be a natural connection, and future work must explore when and how SSO leads to inauthenticity in interpersonal objectification situations.

@@

###Sexual Objectification and the Objectifyer's Gender
The current sample contained a mixture of heterosexual and non-heterosexual women, but all participants were asked to think about and evaluate their partner as a potential dating/romantic partner. We think that hetereosexual women are able to do this with other women as their target---and there is evidence that they might do this readily [@strelan2005women; @puvia2013being]---they may be even more apt to activate social comparison processes [@festinger1954theory] than women who are sexually attracted to other women (non-heterosexual women). This differential psychological process between women with differing sexualities might have served to dampen our ability to detect relationships, adding variability. [Kat: The only other thing I would add re: sexuality limitations are that we didn’t collect/use sexual orientation, so we couldn’t analyze results by that at all/our samples might have differed there.]

@@

##Clinical Implications
The results from the current analysis highlight how subtle forms of sexist discrimination operate, and provide valuable insight into prevention and intervention efforts in both clinical and educational contexts. These results are quite useful for promoting mental health, the creation and maintence of early action programs for girls and young women, and for scholars and practitioners to work intentially to provide the tools necessary to circumvent or mitigate negative effects on self-objectification to combat such experiences.

#Conclusion
The results of this study demonstrate the complex and ambivalent nature of sexual objectification and additionally highlight the psychological and social consequences of such objectification processes on women’s social relationships and well-being. We did not find a significant effect between actor SSO and felt authenticity in the interaction, which suggests that there is not sufficient evidence to support the claim that partner objectification is the cause for the diverse range of negative effects related to interaction inauthenticity. [Move to here: Perhaps women could be amplifying each others' self-objectification as they get ready to go out for the night, *before* the theoretical encounters with men outlined in @gervais2020social occur.]
